---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/jjchern/meta.svg?branch=master)](https://travis-ci.org/jjchern/meta)

# About `meda`

This package provides R functions that replicates the behavior of three Stata commands: (1) `d`, that is, `describe`, (2) `lookfor`, and (3) `codebook, compact`. These commands present **me**ta**da**ta records for datasets in a cleaned way. 

The package is built upon two R packages: `haven`, which provides a labelled class that supports labelled data frames, and `labelled`, which makes it easier to work with 
labelled data frames.

# Installation

Since the `labelled` package is still not up on CRAN, we might also install it as well.

```
devtools::install_github("larmarange/labelled")
devtools::install_github("jjchern/meta")
```

# Usage

```{r}
library(meda)
nlsw88 = haven::read_dta("http://www.stata-press.com/data/r13/nlsw88.dta")

d(nlsw88) # shows variable labels, and whether value label exists for certain variables

# Note that there's a value label for the variable "race", thus we can checkout the values
labelled::val_labels(nlsw88$race)

lookfor(nlsw88, "mar") # search for variables that are related to marriage
```

